### 2020-08-31 benchmarking/benchmarkingVM/ESS_round5b.tex
Results update

% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:56:12
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [\textit{cat}]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [AVMVN+NER+Bactrian+adapt(\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,101.80) --
	(187.28,289.08);

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,183.64) --
	(101.80,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 67.86) --
	(221.22,289.08);

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,217.58) --
	( 67.86,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 33.93) --
	(255.15,289.08);

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,251.51) --
	( 33.93,  0.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (170.87, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,175.57) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (136.94, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,141.64) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (101.01, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56,107.71) {$4\times$};
\definecolor{drawColor}{RGB}{105,105,105}

@@

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 71.42,176.23) --
	( 84.65,176.23);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.92,174.41) --
	( 78.92,177.92);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 78.92,172.34) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.81,162.66) --
	(177.01,162.66);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.00,161.37) --
	(175.00,163.88);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (175.00,157.80) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 83.03,178.79) --
	( 88.54,178.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.94,177.78) --
	( 85.94,179.76);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 85.94,173.93) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 68.08,146.84) --
	( 81.61,146.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 75.77,145.03) --
	( 75.77,148.53);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 75.77,141.98) {$l$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 76.64,170.79) --
	( 89.72,170.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.04,168.73) --
	( 84.04,172.69);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 84.04,167.29) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.14,181.75) --
	(185.74,181.75);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.44,181.29) --
	(185.44,182.19);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.44,178.25) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.17,183.23) --
	(169.48,183.23);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.35,182.63) --
	(168.35,183.81);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.35,179.34) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.41,185.46) --
	(186.36,185.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.41,184.16) --
	(185.41,186.69);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.41,180.60) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.62,191.41) --
	(176.94,191.41);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.78,191.26) --
	(176.78,191.56);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.78,186.55) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.54,175.46) --
	(166.19,175.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.90,174.36) --
	(164.90,176.51);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.90,170.60) {$l$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.00,185.09) --
	(170.90,185.09);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.49,184.25) --
	(169.49,185.90);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.49,181.59) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.97,187.48) --
	(186.70,187.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.34,186.93) --
	(186.34,188.01);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.34,183.98) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.34,156.88) --
	(154.22,156.88);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.82,155.53) --
	(152.82,158.17);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.82,152.99) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,188.93) --
	(188.93,188.93);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.04,188.26) --
	(188.04,189.59);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.04,184.07) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.09,192.48) --
	(182.78,192.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.44,192.24) --
	(182.44,192.72);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.44,187.62) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.78,143.01) --
	(147.93,143.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.41,140.92) --
	(146.41,144.93);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (146.41,138.15) {$l$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.15,153.61) --
	(147.36,153.61);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.89,152.17) --
	(144.89,154.96);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (144.89,150.11) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.56,189.79) --
	(189.29,189.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.93,189.49) --
	(188.93,190.09);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.93,186.29) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.25,166.10) --
	(135.47,166.10);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.45,165.61) --
	(133.45,166.58);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (133.45,162.21) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.59,188.13) --
	(187.96,188.13);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.80,187.38) --
	(186.80,188.87);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.80,183.27) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.33,188.08) --
	(175.07,188.08);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.70,187.92) --
	(174.70,188.24);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.70,183.22) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.97,157.79) --
	(133.26,157.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.21,156.95) --
	(131.21,158.60);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (131.21,152.93) {$l$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.65,160.83) --
	(137.30,160.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.01,159.54) --
	(136.01,162.06);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.01,157.33) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.92,189.83) --
	(189.56,189.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.25,189.51) --
	(189.25,190.15);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.25,186.34) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.90,175.20) --
	(107.68,175.20);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.96,173.42) --
	(104.96,176.85);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (104.96,171.31) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.30,177.06) --
	(182.80,177.06);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.58,176.01) --
	(181.58,178.06);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.58,172.20) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:34
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/hr [\textit{cat}]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/hr [AVMVN+NER+Bactrian+adapt(\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00, 71.00) --
	(218.08,289.08);

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (268.39,289.08) --
	(268.39,197.39) --
	( 71.00,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 47.34) --
	(241.74,289.08);

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (268.39,289.08) --
	(268.39,221.06) --
	( 47.34,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 23.67) --
	(265.41,289.08);

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (268.39,289.08) --
	(268.39,244.72) --
	( 23.67,  0.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.08, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,144.78) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.41, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,121.11) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 90.75, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 97.44) {$4\times$};
\definecolor{drawColor}{RGB}{105,105,105}

@@

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.21,211.39) --
	(197.77,211.39);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.49,211.18) --
	(197.49,211.61);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (197.49,207.50) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.57,213.51) --
	(209.23,213.51);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.90,213.19) --
	(208.90,213.82);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (208.90,210.01) {$\mathcal{L}$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.97,216.96) --
	(203.07,216.96);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.02,216.92) --
	(203.02,217.00);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.02,212.10) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.82,204.83) --
	(193.33,204.83);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.08,204.58) --
	(193.08,205.07);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (193.08,201.33) {$\bar{r}$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.69,206.11) --
	(195.23,206.11);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.96,205.86) --
	(194.96,206.34);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (194.96,201.25) {$l$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.04,212.64) --
	(198.65,212.64);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.35,212.38) --
	(198.35,212.90);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.35,209.14) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.68,214.13) --
	(209.84,214.13);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.76,214.01) --
	(209.76,214.24);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (209.76,210.63) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.61,181.29) --
	(175.42,181.29);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (175.02,180.81) --
	(175.02,181.76);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (175.02,177.40) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.97,203.57) --
	(200.33,203.57);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.15,203.36) --
	(200.15,203.77);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.15,200.07) {$\mathcal{L}$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.18,205.87) --
	(196.32,205.87);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.25,205.81) --
	(196.25,205.93);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.25,201.01) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.45,170.16) --
	(169.30,170.16);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.88,169.66) --
	(168.88,170.65);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.88,166.66) {$\bar{r}$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.19,171.34) --
	(171.03,171.34);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.61,170.86) --
	(170.61,171.80);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.61,166.48) {$l$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.92,178.96) --
	(170.15,178.96);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.55,178.44) --
	(169.55,179.47);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.55,175.46) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.80,203.98) --
	(200.99,203.98);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.89,203.91) --
	(200.89,204.05);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.89,200.48) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (160.27,187.40) --
	(161.12,187.40);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (160.70,187.18) --
	(160.70,187.62);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.70,183.51) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.07,202.56) --
	(198.59,202.56);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.33,202.33) --
	(198.33,202.79);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.33,199.06) {$\mathcal{L}$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.68,202.66) --
	(189.90,202.66);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.79,202.63) --
	(189.79,202.70);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.79,197.80) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.66,181.05) --
	(157.53,181.05);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (157.10,180.80) --
	(157.10,181.30);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (157.10,177.55) {$\bar{r}$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.68,181.59) --
	(159.52,181.59);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (159.10,181.36) --
	(159.10,181.82);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.10,176.73) {$l$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (161.65,183.86) --
	(162.51,183.86);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.09,183.56) --
	(162.09,184.15);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.09,180.36) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.83,203.92) --
	(200.10,203.92);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.96,203.85) --
	(199.96,203.99);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.96,200.42) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.81,179.89) --
	(129.23,179.89);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.06,179.46) --
	(128.06,180.31);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (128.06,176.00) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.96,181.14) --
	(180.68,181.14);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.33,180.91) --
	(180.33,181.37);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.33,177.64) {$\mathcal{L}$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.58,184.80) --
	(156.82,184.80);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.70,184.71) --
	(156.70,184.89);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (156.70,179.94) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.55,153.57) --
	(127.99,153.57);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.81,153.09) --
	(126.81,154.03);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (126.81,150.07) {$\bar{r}$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.51,153.65) --
	(128.85,153.65);

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.72,153.18) --
	(127.72,154.11);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (127.72,148.79) {$l$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.87,168.66) --
	(130.38,168.66);
